\subsection{Text-based Game}
\begin{itemize}
    \item \textbf{Computer Science: "Coding Quest"}
    \begin{itemize}
        \item \textbf{Objective}: Teach students programming concepts and problem-solving skills.
        \item \textbf{Game Structure}:
        \begin{itemize}
            \item \textbf{Narrative}: Players take on the role of a junior developer at a tech company. The company has a major project to deliver, but the lead developer is out sick. The player must step up and solve coding challenges to ensure the project’s success.
            \item \textbf{Mechanics}: Level up by completing coding challenges and debugging tasks. earn achievements and unlock new tools and resources to help you on your journey.
            \begin{itemize}
                \item \textbf{Quests}: Each level represents a different coding challenge or bug-fixing task (e.g., logic problems, debugging code, or algorithm puzzles).
                \item \textbf{Stats}: Track stats like "Coding Skill," "Debugging Efficiency," and "Problem-Solving Ability."
                \item \textbf{Currency}: Players earn "Code Tokens" by completing quests, which can be used to unlock hints, resources, or in-game tools.
            \end{itemize}
        \end{itemize}
        \item \textbf{Learning Outcome}: Students will practice algorithmic thinking, debugging, and programming concepts.
    \end{itemize}

    \item \textbf{Business: "Startup Tycoon"}
    \begin{itemize}
        \item \textbf{Objective}: Teach students the basics of entrepreneurship, marketing, and financial management.
        \item \textbf{Game Structure}:
        \begin{itemize}
            \item \textbf{Narrative}: Players start their own business and must make strategic decisions to grow it into a successful company. They face realistic business scenarios like product launches, marketing campaigns, and investment opportunities.
            \item \textbf{Mechanics}: Leveling up by completing quests and making strategic decisions like hiring employees, manage budgets, and develop new products.
            \begin{itemize}
                \item \textbf{Quests}: Players complete tasks like securing funding, developing a marketing strategy, or negotiating deals with partners.
                \item \textbf{Stats}: Track stats like "Brand Reputation," "Market Share," and "Revenue."
                \item \textbf{Currency}: Use in-game money to invest in product development, marketing, or hire new team members.
            \end{itemize}
        \end{itemize}
        \item \textbf{Learning Outcome}: Students will understand concepts like budgeting, marketing strategies, risk assessment, and financial planning.
    \end{itemize}

    \item \textbf{Physiotherapy: "Rehabilitation Quest"}
    \begin{itemize}
        \item \textbf{Objective}: Teach students the principles of physiotherapy, patient care, and treatment planning.
        \item \textbf{Game Structure}:
        \begin{itemize}
            \item \textbf{Narrative}: The player is a physiotherapist working in a clinic, tasked with creating personalized rehabilitation plans for patients recovering from various injuries or surgeries. They must consider the patient's condition, progress, and specific treatment needs.
            \item \textbf{Mechanics}: 
            \begin{itemize}
                \item \textbf{Quests}: Players take on challenges like selecting appropriate exercises, adjusting treatment plans, and monitoring patient progress to ensure effective rehabilitation.
                \item \textbf{Stats}: Track stats like "Patient Mobility," "Strength Recovery," and "Treatment Effectiveness."
                \item \textbf{Currency}: Manage resources to acquire therapy equipment, schedule sessions, and hire additional specialists.
            \end{itemize}
        \end{itemize}
        \item \textbf{Learning Outcome}: Students will learn about creating customized rehabilitation plans, understanding patient needs, and adapting treatment strategies in physiotherapy.
    \end{itemize}
\end{itemize}