\section{MDA: A Formal Approach to Game Design and Game Research}

\subsection{Authors}
\begin{itemize}
    \item \textbf{Authors:} Robin Hunicke, Marc LeBlanc, Robert Zubek
\end{itemize}

\subsection{Publication}
\begin{itemize}
    \item \textbf{Publication:} AAAI Workshop - Technical Report
    \item \textbf{Date:} January 2004
\end{itemize}

\subsection{Relevant to My Research}
Yes

\subsection{Aim}
The study aims to present the MDA framework, which provides a formal approach to game design and game research. The framework is based on three primary components: Mechanics, Dynamics, and Aesthetics.
\begin{itemize}
    \item \textbf{Mechanics:} The rules and systems that define the game's behavior.
    \item \textbf{Dynamics:} The run-time behavior of the mechanics acting on player inputs and each other.
    \item \textbf{Aesthetics:} The emotional responses evoked in players during gameplay.
\end{itemize}

\subsection{Key Focus Areas}
\begin{itemize}
    \item introduce the MDA framework as a formal approach to game design and research.
    \item discuss the three primary components of the MDA framework: Mechanics, Dynamics, and Aesthetics.
    \item provide examples of how the MDA framework can be applied to game design and research.
\end{itemize}

\subsection{Gaps Addressed}
\begin{itemize}
    \item provide a formal approach to game design and research.
    \item offer a structured framework for analyzing and designing games.
    \item emphasize the importance of aesthetics in game design.
\end{itemize}

\subsection{Gap in the Research}
\begin{itemize}
    \item The study does not provide empirical evidence to support the effectiveness of the MDA framework in game design and research.
    \item The study does not compare the MDA framework with other game design frameworks to highlight its unique features and advantages.
\end{itemize}

\subsection{Findings}
\begin{itemize}
    \item 
\end{itemize}


\subsection{Future Work}
\begin{itemize}
    \item Explore the integration of AI in the MDA framework to enhance the dynamics and aesthetics of games.
    \item Investigate the application of the MDA framework in emerging technologies such as VR, AR, and MR.
    \item Conduct empirical studies to validate the effectiveness of the MDA framework in game design and research.
\end{itemize}

\section{Notes}

\section{Terminlology}
\begin{itemize}
    \item \textbf{MDA Framework:} Mechanics, Dynamics, Aesthetics framework.
    \item \textbf{Mechanics:} The rules and systems that define the game's behavior.
    \item \textbf{Dynamics:} The run-time behavior of the mechanics acting on player inputs and each other.
    \item \textbf{Aesthetics:} The emotional responses evoked in players during gameplay.
\end{itemize}