\section{Towards Automatic Personalized Content Generation for Platform Games}

\subsection{Authors}
\begin{itemize}
    \item \textbf{Authors:} Noor Shaker, Georgios Yannakakis, Julian Togelius
\end{itemize}

\subsection{Publication}
\begin{itemize}
    \item \textbf{Publication:} Proceedings of the Sixth AAAI Conference on Artificial Intelligence and Interactive Digital Entertainment
    \item \textbf{Date:} 2010
\end{itemize}

\subsection{Relevant to My Research}
This paper explores the automatic generation of personalized levels for platform games, which is relevant to research on procedural content generation (PCG) and adaptive gaming.

\subsection{Aim}
The aim of the paper is to design an online game adaptation mechanism that personalizes level design for platform games to optimize player experience based on their playing style.

\subsection{Key Focus Areas}
\begin{itemize}
    \item Procedural content generation (PCG)
    \item Player experience modeling
    \item Real-time adaptation of game content
    \item Evaluation using human and AI players
\end{itemize}

\subsection{Gaps Addressed}
The paper addresses the gap in literature regarding personalized and player-adaptive PCG for platform games, building on previous work to improve prediction models and test adaptation mechanisms.

\subsection{Findings}
\begin{itemize}
    \item The adaptation mechanism optimizes level design for individual players effectively.
    \item Accurate models for predicting player experience based on gameplay data.
    \item Higher predicted fun for AI agents with human-like playing styles.
\end{itemize}

\subsection{Limitations}
\begin{itemize}
    \item Limited number of controllable features used for adaptation.
    \item Experiments were primarily conducted with AI players and a small number of human participants.
\end{itemize}

\subsection{Future Work}
\begin{itemize}
    \item Expanding the set of controllable features.
    \item Testing the model on a larger number of human players.
    \item Investigating the application of the approach to other game genres.
\end{itemize}

\section{Notes}
The research demonstrates the feasibility of personalizing game content in real time to enhance player experience, with future improvements focusing on expanding adaptability and generalization across different types of games.
