\section{Comparing Traditional Teaching and Game-Based Learning using Teacher-Authored Games on Computer Science Education}

\subsection{Authors}
\begin{itemize}
    \item \textbf{Authors:} Daniel López-Fernández, Aldo Gordillo, Pedro P. Alarcón, and Edmundo Tovar
\end{itemize}

\subsection{Publication}
\begin{itemize}
    \item \textbf{Publication:} IEEE Transactions on Education, vol. 64, no. 4, pp. 367–373
    \item \textbf{Date:} 2021
\end{itemize}

\subsection{Relevant to My Research}
This paper provides evidence on the effectiveness of Game-Based Learning (GBL) in computer science education, particularly through the use of teacher-authored educational games. It is highly relevant for exploring how GBL can increase student motivation and match traditional methods in knowledge acquisition.

\subsection{Aim}
The aim of the paper is to compare the instructional effectiveness of traditional teaching and GBL using teacher-authored games, with a focus on student motivation and knowledge acquisition in computer science courses.

\subsection{Key Focus Areas}
\begin{itemize}
    \item Game-Based Learning (GBL)
    \item Teacher-authored educational video games
    \item Comparison of traditional teaching and GBL
    \item Student motivation and knowledge acquisition
\end{itemize}

\subsection{Gaps Addressed}
The paper addresses the lack of empirical studies evaluating the instructional effectiveness of educational video games created by teachers using authoring tools, particularly through Randomized Control Trials (RCTs).

\subsection{Findings}
\begin{itemize}
    \item GBL using teacher-authored games was as effective as traditional teaching in terms of knowledge acquisition.
    \item GBL significantly increased student motivation and engagement compared to traditional teaching.
    \item Most students preferred the GBL approach over traditional lectures.
\end{itemize}

\subsection{Limitations}
\begin{itemize}
    \item The study was limited to two computer science courses at the university level.
    \item GBL's novelty might affect motivation, and overuse could reduce its effectiveness.
\end{itemize}

\subsection{Future Work}
\begin{itemize}
    \item Explore GBL in other knowledge fields beyond computer science.
    \item Investigate GBL's application in promoting practical skills and in self-paced online learning environments.
    \item Study gender differences in the use of educational video games.
\end{itemize}

\section{Notes}
This study provides valuable insights into the effectiveness of GBL, particularly through teacher-authored educational games, showing it can improve student motivation while maintaining similar learning outcomes to traditional teaching.
